Nearest Neighbour Methods for Length of Stay Prediction

### 2015-02-10 papers/paper.tex
Add paragraph to conclusion

>>>>

Although we were able to improve on the work of Dinh et al. \cite{Dinh2013a}
and confirm the
importance of some features they and others found in predicting the LOS for
trauma patients, we did not find a single classifier or feature selector
that was superior to the others but instead observed different combinations
giving better results than others in certain situations. This highlights the
importance of understanding the data and investigating a range of classifiers
and feature selection techniques when approaching any medical data mining
problem, for which our work will become a catalogue.
However, we did find that logistic regression tended to perform well
on both data sets and across a number of feature selection methods, supporting
its common use in deriving classifiers for various medical phenomena.
